Consumer Reviews and Product Discounts:\\ Evidence From Video Games

### 2020-08-08 Analysis/Output/Paper.tex
Packrat snapshot

\title{Consumer Reviews and Product Discounts:\\
Evidence From Video Games}
\author{Dmitry Sorokin}
\date{August 08, 2020}

@@

\begin{table}[t]

\caption{\label{tab:ReviewBinsTable}The mapping between the review score and review bins on Steam}
\centering
\begin{tabular}{lcc}
\toprule
Review Bin & N. of Reviews & Score\\
\midrule
No Score & [0, 10) & -\\
Negative & Any & [0, 40)\\
Mixed & Any & [40, 70)\\
Mostly Positive & Any & [70, 80)\\
Positive & [0, 50) & [80, 100)\\
Very Positive & More than 50 & [80, 100)\\
Overwhelmingly Positive & More than 500 & [95, 100]\\
\bottomrule
\end{tabular}
\end{table}

@@

 {\centering \includegraphics[width=0.75\linewidth,]{/Users/dmitry/Steam_Discounts/Analysis/Output/Paper_files/figure-latex/steamStore}

@@

{\centering \includegraphics{/Users/dmitry/Steam_Discounts/Analysis/Output/Paper_files/figure-latex/example-game-1}

@@

The final sample includes 906 games which I observe for 393 days each,
on average. The main variables in the analysis are the aforementioned
dynamic variables: player count, price, and review score history. An
example observation from the sample is given in Figure
\ref{exampleGame}. For the majority of the games in the sample, the
player count is the highest around the release date, and then it quickly
fades away and oscillates around a smaller level. The player count also
jumps when a discount is given, reflecting the influx of new players.
Games differ a lot in their sizes, as is evident from Figure
\ref{sampleSizeHist}.

@@

{\centering \includegraphics{/Users/dmitry/Steam_Discounts/Analysis/Output/Paper_files/figure-latex/sample-size-hist-1}

@@

As the goal of the paper is to understand if firms use pricing tools in
order to improve their online reputation, a detailed overview of pricing
and review variables is important. A representative game in the sample
never changes its price, but instead occasionally goes on discounts,
slowly increasing their magnitude as the game ages. There are 43
incidents of price change in the data, compared to 6331 discounts. Steam
has a number of rules that regulate price promotions on its platform. A
game can have a launch discount, but, otherwise, it has to wait for two
months since the release before changing its price or giving a discount.
A game can not go on discounts too frequently, and has to wait between
four to six weeks after a price promotion to be able to run a new one.
The duration of a custom discount is restricted to be at least one full
day, and at most two weeks. Besides these custom discounts, that are
fully managed by the firms, Steam has a series of curated discounts,
when the platform invites selected titles to go on a discount. As
\citet{steamDiscounting} explains it, ``while there aren't strict rules,
as a base guideline we tend to focus on the top 10-20\% selling games on
Steam that are positively reviewed and have otherwise proven to be
successful''. Curated promotions are featured prominently on Steam's
main page, and, arguably, lead to more visibility and sales for the
participating titles than custom discounts, which also contribute to
visibility, but typically do not get the front-page promotional slots.
An important type of curated discounts are the so-called ``Seasonal
Sales''--big platform-wide events that take place about four times a
year around major holidays. Figure \ref{seasonalSales} shows that the
biggest sales take place in Winter (Christmas and New Year) and Summer
(July 4), but there are also significant discounts in the Fall
(Halloween and Thanksgiving). Around 64\% of discounts in the sample go
live during a Seasonal Sale. Thus, firms have significant agency when it
comes to running price promotions, but platform regulations and
platform-wide discounts are important determinants of firms' decision to
discount.

@@

{\centering \includegraphics{/Users/dmitry/Steam_Discounts/Analysis/Output/Paper_files/figure-latex/seasonal-sales-1}

@@

The path of the review score of a typical game is quite different from
its price history, in that the review score tends to settle quickly.
Recall that the review score is just the fraction of the positive
reviews among all reviews, so the law of large number implies that this
ratio crystallizes as more reviews flow in. Second plot in Figure
\ref{reviewDescriptivePlots} shows that games tend to receive half of
the reviews they have at the age of 180 days in their first month after
the release. On average across games, the standard deviation of the
review score (out of one hundred) is just 2.2, with a split of 1.83 in
the first thirty days and 1.83 after that. The score is only assigned
once the game reaches 10 reviews, and once can see that 10 reviews is
enough on average keep the score stable. The distribution of games by
bins at the age of 180 days, depicted in Figure
\ref{reviewDescriptivePlots}, is, then, representative of the situation
at other ages.

@@

{\centering \includegraphics{/Users/dmitry/Steam_Discounts/Analysis/Output/Paper_files/figure-latex/review-descriptive-plots-1}

@@

Despite the relative rigidity of the review score, there is enough
transitions between the review bins to make the analysis of pricing
decisions by firms around such transitions possible. Table
\ref{tab:transitionMatrix} describes the transitions between review bins
in the sample. The number of unique games that have changed review
labels in the data is 596, and the number of transitions is 1688.
Sometimes games switch their bins briefly, and go back soon after. The
number of transitions that led to the game spending at least 7 days in
the new bin is 1225. Table \ref{mDiscountTable} describes the state of
the games in the two weeks before their transitions. Discounting does
take place before the transitions, games transition at very different
ages, but tend to have only a limited number of reviews by the time
their review bin changes.

\begin{table}[t]

\caption{\label{tab:transitionMatrix}Transition Probability And Count Matrices}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}{ccccccccccccc}
\toprule
\multicolumn{6}{c}{Probabilities} & \multicolumn{1}{c}{ } & \multicolumn{6}{c}{Counts} \\
\cmidrule(l{3pt}r{3pt}){1-6} \cmidrule(l{3pt}r{3pt}){8-13}
Neg & Mix & M. Pos & Pos & V. Pos & Ov. Pos &   & Neg & Mix & M. Pos & Pos & V. Pos & Ov. Pos\\
\midrule
0 & 100 & 0 & 0 & 0 & 0 & Negative & 0 & 58 & 0 & 0 & 0 & 0\\
24 & 0 & 76 & 0 & 0 & 0 & Mixed & 60 & 0 & 189 & 0 & 0 & 0\\
0 & 43 & 0 & 25 & 33 & 0 & M. Positive & 0 & 245 & 0 & 141 & 188 & 0\\
0 & 0 & 40 & 0 & 60 & 0 & Positive & 0 & 2 & 207 & 0 & 310 & 0\\
0 & 0 & 84 & 0 & 0 & 16 & V. Positive & 0 & 0 & 220 & 0 & 0 & 43\\
0 & 0 & 0 & 0 & 100 & 0 & Ov. Positive & 0 & 0 & 0 & 0 & 25 & 0\\
\bottomrule
\end{tabular}}
\end{table}

@@

{\centering \includegraphics{/Users/dmitry/Steam_Discounts/Analysis/Output/Paper_files/figure-latex/transition-discount-plot-1}

@@

The departing point of the analysis is Figure
\ref{discountsTransitions}, which shows that transitions between review
labels are very often preceded by discounts. The graph shows that two
weeks prior to a transition only 15\% of games were on a discount, a
number close to the sample average, but that this number more than
doubles to around 35\% one day before the label change. Regression
analysis controlling for review label, number of reviews, age, day of
the week and week time effects, as well as time since the previous
discount, confirms that the association depicted in Figure
\ref{discountsTransitions} is robust (see Table \ref{transitionReg} in
the Appendix). A game is approximately 8 pp more likely to be on a
discount on the day of the transition than it is two weeks prior to it,
and it is 16 pp less likely to be on a discount two weeks following the
transition. Given that the probability for a game to be on a discount on
a random day is 16\% in the sample, these effects amount to 3\% and 7\%
changes in the daily probability of a discount, which is quite sizable.

@@

As the example above shows, it is impossible to consider proximity to a
positive transition without taking into account the proximity to a
negative transition, at least for moderately sized games. If firms'
strategies for these types of transitions are different, then studying
such transitions separately could attenuate the effect of the proximity
to, say, a positive transition, on the discount probability: a firm that
is close to upgrading its review bin might not give a discount not
because it is a bad way to accomplish that transition, but because that
firm is at the same time close to downgrading its review bin, and might
prefer to exercise prudence. For this reason, I define two ``treatment''
variables of interest. Game \(i\) at date \(t\) is said to be close to a
positive transition, \(T_{it}^+ = 1\), if its proximity to a positive
transition is less than or equal to 14 days. Similarly, game \(i\) at
date \(t\) is said to be close to a negative transition,
\(T_{it}^- = 1\), if its proximity to a positive transition is less than
or equal to 14 days. The 14 cutoff is inspired by the maximum duration
of custom discounts on Steam, and the patterns of discounting around
successful transitions, depicted in Figure \ref{discountsTransitions}.
To estimate the effect of being close to a review transition on the
discounting behavior, I then estimate the following model:
\begin{equation}\label{potTransitionsReg}
disc_{it} = \beta^+ T_{it}^+ + \beta^- T_{it}^- + X_{it}\beta + f_i + \tau_t + \varepsilon_{it},
\end{equation}

@@

Notice that the inclusion of both the distance to a potential positive,
and a potential negative, transition in the regression drops all
observations from the lowest (``Negative'') and the highest
(``Overwhelmingly Positive'') review bins, as for games in those bins
only one way of review transition is possible. However, given that the
proportion of such observations in the sample is quite small, this is
not a big concern. The analysis also excludes the observations with a
``No Review Score'' label, as I do not want to take a stance on what
constitutes an improvement or a deterioration of the review score for
such games. The results of estimating Equation \ref{potTransitionsReg}
are presented in Table \ref{potentialTransitionsResults}. The first
column is the full specification that uses all observations in the
sample (except the omissions just mentioned). The second column uses a
more stringent definition of proximity to a transition, requiring a game
to be 7, rather than 14, days away from a potential transition to be
counted as being ``close to a transition''. The third column uses only
transitions between ``Mixed'', ``Mostly Positive'', and ``Positive''
labels, as these are the transitions that rely on the review score only,
while ``Very Positive'' and ``Overwhelmingly Positive'' require both a
certain review score, and a certain number of
reviews.\footnote{Technically, a game improving its review score from 79\% to 80\% can transition to both “Positive” and “Very Positive”, so the results in the third column bundle together these types of transitions.}.
\citet{SorokinStevens20} exclusively uses these simple review bins in
their regression discontinuity analysis, precisely in order to avoid the
complications that arise from double thresholds required for ``Very
Positive'' and ``Overwhelmingly Positive''.

The results in Table \ref{potentialTransitionsResults} unequivocally
support the hypothesis that proximity to a review bin upgrade increases
firms' willingness to run a price promotion. Measured against the 16\%
probability for a random game-day pair from the sample to have a
discount\footnote{The corresponding number for the games in the treatment group is 17.},
the effects constitute a 4-6\% increase in the daily probability of a
discount. The uncertainty about the sign and the significance of the
proximity to a potential negative transition is resolved in favor of the
prudent approach on the firms' side: the results suggest that firms
under a risk of deteriorating their review label are 4-5\% less likely
to go on a discount, albeit the effect is only present in two out of
three specifications.

>>>>

\title{Consumer Reviews and Product Discounts:\\
Evidence From Video Games}
\author{Dmitry Sorokin}
\date{\texttt{r\ format(Sys.time(),\ \textquotesingle{}\%B\ \%d,\ \%Y\textquotesingle{})}}

@@

\begin{table}

\caption{\label{tab:ReviewBinsTable}The mapping between the review score and review bins on Steam}
\centering
\begin{tabular}[t]{lcc}
\toprule
Review Bin & N. of Reviews & Score\\
\midrule
No Score & [0, 10) & -\\
Negative & Any & [0, 40)\\
Mixed & Any & [40, 70)\\
Mostly Positive & Any & [70, 80)\\
Positive & [0, 50) & [80, 100)\\
Very Positive & More than 50 & [80, 100)\\
Overwhelmingly Positive & More than 500 & [95, 100]\\
\bottomrule
\end{tabular}
\end{table}

@@

 {\centering \includegraphics[width=0.75\linewidth,]{/Users/dmitry/Steam_Discounting/Analysis/Output/Paper_files/figure-latex/steamStore}

@@

{\centering \includegraphics{/Users/dmitry/Steam_Discounting/Analysis/Output/Paper_files/figure-latex/example-game-1}

@@

The final sample includes \texttt{r\ info{[},\ .N{]}} games which I
observe for
\texttt{r\ panel{[},\ max(age),\ by\ =\ ID{]}{[},\ round(mean(V1)){]}}
days each, on average. The main variables in the analysis are the
aforementioned dynamic variables: player count, price, and review score
history. An example observation from the sample is given in Figure
\ref{exampleGame}. For the majority of the games in the sample, the
player count is the highest around the release date, and then it quickly
fades away and oscillates around a smaller level. The player count also
jumps when a discount is given, reflecting the influx of new players.
Games differ a lot in their sizes, as is evident from Figure
\ref{sampleSizeHist}.

@@

{\centering \includegraphics{/Users/dmitry/Steam_Discounting/Analysis/Output/Paper_files/figure-latex/sample-size-hist-1}

@@

As the goal of the paper is to understand if firms use pricing tools in
order to improve their online reputation, a detailed overview of pricing
and review variables is important. A representative game in the sample
never changes its price, but instead occasionally goes on discounts,
slowly increasing their magnitude as the game ages. There are
\texttt{r\ panel{[}discount==F,\ diff(price),\ by\ =\ ID{]}{[}V1\textgreater{}0,\ .N{]}}
incidents of price change in the data, compared to
\texttt{r\ panel{[}discNew==T,\ .N{]}} discounts. Steam has a number of
rules that regulate price promotions on its platform. A game can have a
launch discount, but, otherwise, it has to wait for two months since the
release before changing its price or giving a discount. A game can not
go on discounts too frequently, and has to wait between four to six
weeks after a price promotion to be able to run a new one. The duration
of a custom discount is restricted to be at least one full day, and at
most two weeks. Besides these custom discounts, that are fully managed
by the firms, Steam has a series of curated discounts, when the platform
invites selected titles to go on a discount. As \citet{steamDiscounting}
explains it, ``while there aren't strict rules, as a base guideline we
tend to focus on the top 10-20\% selling games on Steam that are
positively reviewed and have otherwise proven to be successful''.
Curated promotions are featured prominently on Steam's main page, and,
arguably, lead to more visibility and sales for the participating titles
than custom discounts, which also contribute to visibility, but
typically do not get the front-page promotional slots. An important type
of curated discounts are the so-called ``Seasonal Sales''--big
platform-wide events that take place about four times a year around
major holidays. Figure \ref{seasonalSales} shows that the biggest sales
take place in Winter (Christmas and New Year) and Summer (July 4), but
there are also significant discounts in the Fall (Halloween and
Thanksgiving). Around
\texttt{r\ \ round(panel{[}discSeason==T\ \&\ discNew\ ==\ T,\ .N{]}/panel{[}discNew==T,\ .N{]}*100)}\%
of discounts in the sample go live during a Seasonal Sale. Thus, firms
have significant agency when it comes to running price promotions, but
platform regulations and platform-wide discounts are important
determinants of firms' decision to discount.

@@

{\centering \includegraphics{/Users/dmitry/Steam_Discounting/Analysis/Output/Paper_files/figure-latex/seasonal-sales-1}

@@

The path of the review score of a typical game is quite different from
its price history, in that the review score tends to settle quickly.
Recall that the review score is just the fraction of the positive
reviews among all reviews, so the law of large number implies that this
ratio crystallizes as more reviews flow in. Second plot in Figure
\ref{reviewDescriptivePlots} shows that games tend to receive half of
the reviews they have at the age of 180 days in their first month after
the release. On average across games, the standard deviation of the
review score (out of one hundred) is just
\texttt{r\ round(panel{[},\ sd(score,\ na.rm=T),\ by\ =\ ID{]}{[},\ mean(V1,\ na.rm\ =\ T){]},\ 2)},
with a split of
\texttt{r\ round(panel{[}age\ \textless{}=\ 30,\ sd(score,\ na.rm=T),\ by\ =\ ID{]}{[},\ mean(V1,\ na.rm\ =\ T){]},\ 2)}
in the first thirty days and
\texttt{r\ round(panel{[}age\ \textgreater{}\ 30,\ sd(score,\ na.rm=T),\ by\ =\ ID{]}{[},\ mean(V1,\ na.rm\ =\ T){]},\ 2)}
after that. The score is only assigned once the game reaches 10 reviews,
and once can see that 10 reviews is enough on average keep the score
stable. The distribution of games by bins at the age of 180 days,
depicted in Figure \ref{reviewDescriptivePlots}, is, then,
representative of the situation at other ages.

@@

{\centering \includegraphics{/Users/dmitry/Steam_Discounting/Analysis/Output/Paper_files/figure-latex/review-descriptive-plots-1}

@@

Despite the relative rigidity of the review score, there is enough
transitions between the review bins to make the analysis of pricing
decisions by firms around such transitions possible. Table
\ref{tab:transitionMatrix} describes the transitions between review bins
in the sample. The number of unique games that have changed review
labels in the data is
\texttt{r\ transitions{[},\ unique(ID){]}\ \%\textgreater{}\%\ length},
and the number of transitions is \texttt{r\ transitions{[},\ .N{]}}.
Sometimes games switch their bins briefly, and go back soon after. The
number of transitions that led to the game spending at least 7 days in
the new bin is
\texttt{r\ transitions{[}(is.na(dur)\ \textbar{}\ dur\ \textgreater{}=\ 7),\ .N{]}}.
Table \ref{mDiscountTable} describes the state of the games in the two
weeks before their transitions. Discounting does take place before the
transitions, games transition at very different ages, but tend to have
only a limited number of reviews by the time their review bin changes.

\begin{table}

\caption{\label{tab:transitionMatrix}Transition Probability And Count Matrices}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{ccccccccccccc}
\toprule
\multicolumn{6}{c}{Probabilities} & \multicolumn{1}{c}{ } & \multicolumn{6}{c}{Counts} \\
\cmidrule(l{3pt}r{3pt}){1-6} \cmidrule(l{3pt}r{3pt}){8-13}
Neg & Mix & M. Pos & Pos & V. Pos & Ov. Pos &   & Neg & Mix & M. Pos & Pos & V. Pos & Ov. Pos\\
\midrule
0 & 100 & 0 & 0 & 0 & 0 & Negative & 0 & 58 & 0 & 0 & 0 & 0\\
24 & 0 & 76 & 0 & 0 & 0 & Mixed & 60 & 0 & 189 & 0 & 0 & 0\\
0 & 43 & 0 & 25 & 33 & 0 & M. Positive & 0 & 245 & 0 & 141 & 188 & 0\\
0 & 0 & 40 & 0 & 60 & 0 & Positive & 0 & 2 & 207 & 0 & 310 & 0\\
0 & 0 & 84 & 0 & 0 & 16 & V. Positive & 0 & 0 & 220 & 0 & 0 & 43\\
0 & 0 & 0 & 0 & 100 & 0 & Ov. Positive & 0 & 0 & 0 & 0 & 25 & 0\\
\bottomrule
\end{tabular}}
\end{table}

@@

{\centering \includegraphics{/Users/dmitry/Steam_Discounting/Analysis/Output/Paper_files/figure-latex/transition-discount-plot-1}

@@

The departing point of the analysis is Figure
\ref{discountsTransitions}, which shows that transitions between review
labels are very often preceded by discounts. The graph shows that two
weeks prior to a transition only 15\% of games were on a discount, a
number close to the sample average, but that this number more than
doubles to around 35\% one day before the label change. Regression
analysis controlling for review label, number of reviews, age, day of
the week and week time effects, as well as time since the previous
discount, confirms that the association depicted in Figure
\ref{discountsTransitions} is robust (see Table \ref{transitionReg} in
the Appendix). A game is approximately
\texttt{r\ round(reg1\$coefficients{[}2{]}*14*100)} pp more likely to be
on a discount on the day of the transition than it is two weeks prior to
it, and it is \texttt{r\ round(-reg1\$coefficients{[}3{]}*14*100)} pp
less likely to be on a discount two weeks following the transition.
Given that the probability for a game to be on a discount on a random
day is
\texttt{r\ round(panel{[},\ mean((discount\ \textgreater{}\ 0),\ na.rm=T){]}*100)}\%
in the sample, these effects amount to
\texttt{r\ round(100*(reg1\$coefficients{[}2{]}/panel{[},\ mean((discount\ \textgreater{}\ 0),\ na.rm=T){]}))}\%
and
\texttt{r\ round(100*(-reg1\$coefficients{[}3{]}/panel{[},\ mean((discount\ \textgreater{}\ 0),\ na.rm=T){]}))}\%
changes in the daily probability of a discount, which is quite sizable.

@@

As the example above shows, it is impossible to consider proximity to a
positive transition without taking into account the proximity to a
negative transition, at least for moderately sized games. If firms'
strategies for these types of transitions are different, then studying
such transitions separately could attenuate the effect of the proximity
to, say, a positive transition, on the discount probability: a firm that
is close to upgrading its review bin might not give a discount not
because it is a bad way to accomplish that transition, but because that
firm is at the same time close to downgrading its review bin, and might
prefer to exercise prudence. For this reason, I define two ``treatment''
variables of interest. Game \(i\) at date \(t\) is said to be close to a
positive transition, \(T_{it}^+ = 1\), if its proximity to a positive
transition is less than or equal to \texttt{r\ 2*band} days. Similarly,
game \(i\) at date \(t\) is said to be close to a negative transition,
\(T_{it}^- = 1\), if its proximity to a positive transition is less than
or equal to \texttt{r\ 2*band} days. The \texttt{r\ 2*band} cutoff is
inspired by the maximum duration of custom discounts on Steam, and the
patterns of discounting around successful transitions, depicted in
Figure \ref{discountsTransitions}. To estimate the effect of being close
to a review transition on the discounting behavior, I then estimate the
following model: \begin{equation}\label{potTransitionsReg}
disc_{it} = \beta^+ T_{it}^+ + \beta^- T_{it}^- + X_{it}\beta + f_i + \tau_t + \varepsilon_{it},
\end{equation}

@@

Notice that the inclusion of both the distance to a potential positive,
and a potential negative, transition in the regression drops all
observations from the lowest (``Negative'') and the highest
(``Overwhelmingly Positive'') review bins, as for games in those bins
only one way of review transition is possible. However, given that the
proportion of such observations in the sample is quite small, this is
not a big concern. The analysis also excludes the observations with a
``No Review Score'' label, as I do not want to take a stance on what
constitutes an improvement or a deterioration of the review score for
such games. The results of estimating Equation \ref{potTransitionsReg}
are presented in Table \ref{potentialTransitionsResults}. The first
column is the full specification that uses all observations in the
sample (except the omissions just mentioned). The second column uses a
more stringent definition of proximity to a transition, requiring a game
to be \texttt{r\ band}, rather than \texttt{r\ 2*band}, days away from a
potential transition to be counted as being ``close to a transition''.
The third column uses only transitions between ``Mixed'', ``Mostly
Positive'', and ``Positive'' labels, as these are the transitions that
rely on the review score only, while ``Very Positive'' and
``Overwhelmingly Positive'' require both a certain review score, and a
certain number of
reviews.\footnote{Technically, a game improving its review score from 79\% to 80\% can transition to both “Positive” and “Very Positive”, so the results in the third column bundle together these types of transitions.}.
\citet{SorokinStevens20} exclusively uses these simple review bins in
their regression discontinuity analysis, precisely in order to avoid the
complications that arise from double thresholds required for ``Very
Positive'' and ``Overwhelmingly Positive''.

The results in Table \ref{potentialTransitionsResults} unequivocally
support the hypothesis that proximity to a review bin upgrade increases
firms' willingness to run a price promotion. Measured against the
\texttt{r\ round(panel{[},\ mean((discount\ \textgreater{}\ 0),\ na.rm=T){]}*100)}\%
probability for a random game-day pair from the sample to have a
discount\textbackslash footnote\{The corresponding number for the games
in the treatment group is
\texttt{r\ round(100*panel{[}ID\ \%in\%\ panel{[}pos.treatment\ ==\ 1,\ unique(ID){]},\ mean((discount\ \textgreater{}\ 0),\ na.rm\ =\ T){]})}.\},
the effects constitute a
\texttt{r\ round(100*(reg3\$coefficients{[}1{]}/panel{[},\ mean((discount\ \textgreater{}\ 0),\ na.rm=T){]}))}-\texttt{r\ round(100*(reg1\$coefficients{[}1{]}/panel{[},\ mean((discount\ \textgreater{}\ 0),\ na.rm=T){]}))}\%
increase in the daily probability of a discount. The uncertainty about
the sign and the significance of the proximity to a potential negative
transition is resolved in favor of the prudent approach on the firms'
side: the results suggest that firms under a risk of deteriorating their
review label are
\texttt{r\ -round(100*(reg3\$coefficients{[}2{]}/panel{[},\ mean((discount\ \textgreater{}\ 0),\ na.rm=T){]}))}-\texttt{r\ -round(100*(reg1\$coefficients{[}2{]}/panel{[},\ mean((discount\ \textgreater{}\ 0),\ na.rm=T){]}))}\%
less likely to go on a discount, albeit the effect is only present in
two out of three specifications.
